Model

### 2020-02-11 stats/model.Rmd
model comparison example for MH to check

# Model utilities

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(bigmemory)
library(langcog)

@@

```{r rsaUtils}
rsaUtils <- '
var all_objects = [
{ shape: "novel_object"},  
{ shape: "familiar_object"}
]

var labels = ["novel_word","familiar_word"]

var lexicon1 = function(utterance, obj, sem_knowledge){
  utterance.label == "novel_word" ? obj.shape == "novel_object" :
  utterance.label == "familiar_word" ? flip(sem_knowledge) ? 
    obj.shape == "familiar_object" :  
  flip() ? obj.shape == "familiar_object" : obj.shape == "novel_object" : 
  true
}

var lexicon2 = function(utterance, obj, sem_knowledge){
  utterance.label == "novel_word" ? obj.shape == "familiar_object" :
  utterance.label == "familiar_word" ? flip(sem_knowledge) ? 
    obj.shape == "familiar_object" : 
  flip() ? obj.shape == "familiar_object" : obj.shape == "novel_object" : 
  true
}

var lexiconObjects = {
"novel_word = novel_object": {
novel_object: "novel_word", familiar_object: "familiar_word"
},
"novel_word = familiar_object": {
novel_object: "familiar_word", familiar_object: "familiar_word"
},
}

var lexiconObject = {
"novel_word = novel_object": lexicon1,
"novel_word = familiar_object" : lexicon2
}

var utterancePrior = function(){ return uniformDraw([ {label: "novel_word"}, {label: "familiar_word"}]) }

var LexiconPrior = Categorical({vs: ["novel_word = novel_object","novel_word = familiar_object" ], ps: [1, 1]})

var addNoise = function(dist, noiseParam){
   Infer({model: function(){ 
      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
    }
   })
}

var foreach = function(fn, lst) {
    var foreach_ = function(i) {
        if (i < lst.length) {
            fn(lst[i]);
            foreach_(i + 1);
        }
    };
    foreach_(0);
};

var logistic = function(x) {1 / (1 + Math.exp(-x))}

var levels = function(df, label){
  return _.uniq(_.map(df, label));
}
'
```

```{r rsa model}
rsaModel <- '
var literalListener = cache(function(utterance, priorProbs, sem_knowledge){
  Infer({method: "enumerate", model: function(){
    var lexiconName = sample(LexiconPrior); 
    var lexicon = lexiconObject[lexiconName];
    var obj = sample( Categorical({vs: all_objects, ps: [.5,.5]}));
    if ("label" in utterance) {
      var truthValue = lexicon(utterance, obj, sem_knowledge);
      condition(truthValue)
    }
    return obj.shape 
  }})
}, 10000)

var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality, sem_knowledge){
  Infer({method: "enumerate", model: function(){
    var utterance = utterancePrior();
    var L0 = literalListener(utterance, priorProbs, sem_knowledge);
    factor(speakerOptimality * L0.score(obj.shape))
    return utterance
  }})
}, 10000)

var pragmaticListener = cache(function(utterance, priorProbs, speakerOptimality, sem_knowledge){
  Infer({method: "enumerate", model: function(){
    var lexiconName = sample(LexiconPrior);
    var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
    var S1 = speaker(obj, lexiconName, priorProbs, speakerOptimality, sem_knowledge);
    observe(S1, utterance)
    return obj.shape == "novel_object" ? 1 : 0
  }})
}, 10000)

# Model

## Combination Model

```{r work in progress}
sem_subj_str <- '

var data = dataFromR.data
var priorData = dataFromR.data

var familiars = levels(data, "item")
var subjects = levels(data, "subid")
var priorSubjects = levels(priorData, "subid")

//////////////// Prior ////////////////////////

  query.add(["parameter","parameters", "prior"], [prior_int, prior_slope])
  query.add(["parameter","sigma", "prior"], ["NA", prior_subject_sigma])

//////////////// Semantic knowledge and speaker optimality ////////////////////////

  var sampleItemParameters = function(itemName) { 
    return [itemName, {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
        slope: gaussianDrift({
          mu: globalLineParameters.slope, 
          sigma: itemVariability.slope, 
          width: 0.5
        })
      }]
  }

  // {papaya: {int, slope}, bread: {int, slope}, ... }
  var all_item_parameters = _.fromPairs(map(sampleItemParameters, familiars))

  // want something that favors smaller values
  var subject_sigma = uniformDrift({a: 0, b:1, width: 0.1})

  var sampleLinguisticCompetence = function(age){
    return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.1 })
  }

  foreach(function(subid){
      var subjectData = _.filter(data, {subid: subid})
      var subj_age = subjectData[0].age
      var subj_linguistic_competence = sampleLinguisticCompetence(subj_age)

     // display("age = " + subj_age + " ... intercept = " + subj_linguistic_competence)

      // question: should we use age here instead of the random intercept? or a different random intercept?

  var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * subj_age

      // each row is a different item
      foreach(function(row){

        var itemLineParameters = all_item_parameters[row.item]

        var sem_knowledge = logistic(itemLineParameters.intercept + 
            itemLineParameters.slope * subj_linguistic_competence)

        // if you want to save predictions, make sure to record subid because these predictions are for this particular subid
        // query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])

      }, subjectData)

    // comment out to save memory
  //  query.add(["parameter","subj_intercept", subid], [subjectData[0].age, subj_linguistic_competence])

  }, subjects)

//////////////// Model predictions and combination ////////////////////////

var noise = uniformDrift({a: 0, b:1, width: 0.1})

var all_log_likes = map(function(row) {

  var priorReg = logistic(prior_int + prior_slope * row.age)

  var cond = row.condition

  var prior = function(cnd){
    var cndPrior = cnd == "congruent" ? [priorReg, 1-priorReg] : [1-priorReg, priorReg] ;
    return cndPrior
  }

  var priorComb = prior(cond)

  var itemLineParameters = all_item_parameters[row.item]

  var sem_knowledge = logistic(itemLineParameters.intercept + 
                               itemLineParameters.slope * row.age)

  var global_sem_knowledge = logistic(globalLineParameters.intercept + 
                               globalLineParameters.slope * row.age)

  var speakerOptimality = speakerOptimalityParameters.intercept  + 
      speakerOptimalityParameters.slope * row.age

  var pragModelPredictions = pragmaticListener({label: "novel_word"}, 
                                               priorComb, speakerOptimality, 
                                               sem_knowledge)

  var noisyPragModelPredictions = addNoise(pragModelPredictions, noise)

  var globalPragModelPredictions = pragmaticListener({label: "novel_word"}, 
                                               priorComb, speakerOptimality, 
                                               global_sem_knowledge)

   var noisyGlobalPragModelPredictions = addNoise(globalPragModelPredictions, noise)

   var flatModelPredictions = pragmaticListener({label: "novel_word"}, 
                                               [.5, .5], speakerOptimality, 
                                               sem_knowledge)

   var noisyFlatModelPredictions = addNoise(flatModelPredictions, noise)

  var priorOnlyModelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: priorComb}));
      return obj.shape == "novel_object" ? 1 : 0
       }})

  var noisyPriorOnlyModelPredictions = addNoise(priorOnlyModelPredictions, noise)

  query.add(["modelPrediction","pragmatic","free", row.alignment, row.item, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])

//  query.add(["modelPrediction","globalPrag","free", row.alignment, row.item, row.subid], [row.age, Math.exp(globalPragModelPredictions.score(1))])

  return {
    prag: pragModelPredictions.score(row.correct),
    noisePrag: noisyPragModelPredictions.score(row.correct),

    globalPrag: globalPragModelPredictions.score(row.correct),
    noiseGlobalPrag: noisyGlobalPragModelPredictions.score(row.correct),

    flat: flatModelPredictions.score(row.correct),
    noiseFlat: noisyFlatModelPredictions.score(row.correct),

    priorOnly: priorOnlyModelPredictions.score(row.correct),
    noisePriorOnly: noisyPriorOnlyModelPredictions.score(row.correct)
  }

}, dataFromR.comb_data)

var log_likelihood_prag = sum(_.map(all_log_likes, "prag"))
var log_likelihood_prag_noise = sum(_.map(all_log_likes, "noisePrag"))

var log_likelihood_prag_global = sum(_.map(all_log_likes, "globalPrag"))
var log_likelihood_prag_global_noise = sum(_.map(all_log_likes, "noiseGlobalPrag"))

var log_likelihood_flat = sum(_.map(all_log_likes, "flat"))
var log_likelihood_flat_noise = sum(_.map(all_log_likes, "noiseFlat"))

var log_likelihood_prior_only = sum(_.map(all_log_likes, "priorOnly"))
var log_likelihood_prior_only_noise = sum(_.map(all_log_likes, "noisePriorOnly"))

query.add(["log_like", "pragmatics", "parameter_free"], ["NA", log_likelihood_prag])
query.add(["log_like", "pragmatics", "noise"], ["NA", log_likelihood_prag_noise])

query.add(["log_like", "pragmatics_global", "parameter_free"], ["NA", log_likelihood_prag_global])
query.add(["log_like", "pragmatics_global", "noise"], ["NA", log_likelihood_prag_global_noise])

query.add(["log_like", "flat_prior", "parameter_free"], ["NA", log_likelihood_flat])
query.add(["log_like", "flat_prior", "noise"], ["NA", log_likelihood_flat_noise])

query.add(["log_like", "prior_only", "parameter_free"], ["NA", log_likelihood_prior_only])
query.add(["log_like", "prior_only", "noise"], ["NA", log_likelihood_prior_only_noise])

  foreach(function(item){
    var itemLineParameters = all_item_parameters[item]
    query.add(["parameter","items", item], [itemLineParameters.intercept, itemLineParameters.slope])
  }, familiars)

  query.add(["parameter","parameters","speaker_optimality"], [speakerOptimalityParameters.intercept, speakerOptimalityParameters.slope])
  query.add(["parameter","parameters", "global_sem"], [globalLineParameters.intercept, globalLineParameters.slope])
  query.add(["parameter","sigma", "global_sem_sigmas"], [itemVariability.intercept, itemVariability.slope])
  query.add(["parameter","sigma", "global_subject_sigmas"], ["NA", subject_sigma])

  return query 
}

var header = "iteration,a,b,c,d,e,f,g,h"

var randomNumberForFile = Math.round(uniform(0, 1000))

var callback = webpplSampleWriter.streamQueryCSV("../saves/model/samples"+randomNumberForFile+".csv", header);

Infer({model,
      samples: 10,
      burn: 10,
      verbose: T,
      lag: 1,
      verboseLag: 1000,
      method: "incrementalMH",
      onlyMAP: true,
      callbacks: [callback]});
'
```

## Model run

```{r}
sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb, prior_data = prior_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 2,
  cores = 2,
  packages = c("webppl_packages/webppl-sample-writer")
)
```

```{r}
ggplot(log_like_model_2_free, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=-1150, yend=logP), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  #facet_grid(~parameter)+
  #ylim(-1750,-1150)+
  scale_color_ptol(breaks=c("pragmatics","pragmatics_global","prior_only","flat_prior"),
                     labels=c("Pragmatic", "Pragmatic global","Prior only","Flat prior"))+
    theme(axis.text.x=element_blank(), 
        axis.ticks.x=element_blank())
```

```{r}
ggsave("../graphs/like_talk_free.png", width = 4, height = 2.5, scale = 1.5)
```

## Summarizing parameters

@@

subject_sigma <- readRDS("../saves/subject_sigma_re.rds")

item_params <- bind_rows(
  readRDS("../saves/item_params.rds")%>%mutate(run = "no re"),
  readRDS("../saves/item_params_re.rds")%>%mutate(run = "re")
)

global_params <- bind_rows(
  readRDS("../saves/global_params.rds")%>%mutate(run = "no re"),
  readRDS("../saves/global_params_re.rds")%>%mutate(run = "re")
)

item_sigma <- bind_rows(
  readRDS("../saves/item_sigmas.rds")%>%mutate(run = "no re"),
  readRDS("../saves/item_sigma_re.rds")%>%mutate(run = "re")
)

model_pred <- bind_rows(
    readRDS("../saves/model_pred.rds")%>%mutate(run = "no re")%>%filter(model == "pragmatic"),
    readRDS("../saves/model_pred_re.rds")%>%mutate(run = "re")%>%filter(model == "pragmatic")
)

x <- readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")

xx <- x %>%
  filter(!(Parameter %in% c("noise"))) %>%
  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
  mutate(model = "prior_only_noise")%>%
  group_by(model,age,item, alignment) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         source = "Model")

#### summaries
item_params_summary <- item_params %>%
  group_by(run, item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

global_params_summary <- global_params %>%
  group_by (run,parameter,type)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

subject_sigma_summary <- subject_sigma %>%
  group_by (parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

@@

```{r}
plotg_subj_sigma <- ggplot(subject_sigma, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Subject Sigma")+
  theme_few()

plotg_subj_sigma
```

select_id <- me_model_data %>%
  filter(age < 1.3,
         age >1)%>%
  group_by(age,subid)%>%
  summarise(mean = mean(correct))%>%
  mutate(id = subid)

subject_params <- subject_params %>%
  left_join(select_id)%>%
  filter(mean != "NA")%>%
  ungroup()

ggplot(subject_params, aes(x = int, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  geom_vline(aes(xintercept = age), size = 1.5)+
  #geom_vline(aes(xintercept = mean), size = 1.5, col = "red")+
  facet_grid(id+ round(mean,2)~.)+
  xlab("Subject Intercept")+
  theme_few()

#ggsave("../graphs/subj_intercept.pdf", width = 5, height = 8, scale = 1.5)

@@

```{r}
aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)

aoa_ratings <- aoa_ratings_all %>%
  filter(Word %in% item_params_summary$item )%>%
  mutate(mean_aoa = as.numeric(Rating.Mean),
         item = Word)%>%
  select(item,mean_aoa)

plot_sem_know <- item_params_summary%>%
  select(-uci,-lci)%>%
  spread(parameter, -item) %>%
  left_join(expand.grid(
      age = unique(me_model_data$age),
      item = unique(me_model_data$familiar)), .) %>%
  mutate(sem_know = plogis(int + slope * age)) %>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

@@

model_pred_prag <- readRDS("../saves/model_pred_prag.rds")

@@

x <- sample(1:length(unique(model_pred_prag$iteration)), 100)

plot_model_prag_line <- model_pred_prag%>%
  filter(iteration %in% x)

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(data = plot_model_prag_line, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .05)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 2)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)

@@

```{r}
ggsave("../graphs/pred_model_data.pdf", width = 10, height = 4, scale = 1)
```

### Global pragmatic model

model_pred_global<- readRDS("../saves/model_pred_global.rds")

plot_model_pred_global <- model_pred_global%>%
  group_by(alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred_global, aes(x=age+2,y = mean, col = alignment), size = 1)+
  geom_ribbon(data = plot_model_pred_global, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol()+
  scale_fill_ptol()
```

@@

```{r}
binnned_data <- data_comb%>%
  group_by(subage, alignment, item)%>%
  summarize(k = sum(correct), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         data_mean = (a-1)/(a+b-2),
         data_ci_lower  = qbeta(.025, a, b),
         data_ci_upper = qbeta(.975, a, b),
         age = factor(subage))%>%
  select(-a,-b,-n,-k)

cor_prag <- model_pred_prag%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model,alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

# cor_prag_chain <- model_pred_prag%>%
#   mutate(age = as.numeric(age) + min(data_comb$age_num),
#          age = cut(age, 
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(chain, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))

cor_global <- model_pred_global%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

model_pred_flat<- readRDS("../saves/model_pred_flat.rds")

cor_flat <- model_pred_flat%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

model_pred_prior<- readRDS("../saves/model_pred_prior.rds")

# cor_prior <- model_pred_prior%>%
#   mutate(age = as.numeric(age) + min(data_comb$age_num),
#          age = cut(age, 
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))

cor_model_pred <- bind_rows(
  #cor_prag_chain,
  cor_prag,
  cor_global,
  cor_flat,
  cor_prior
)

plot_cor_model_pred <- cor_model_pred %>%
  left_join(
    bind_rows(
      # binnned_data%>%mutate(model = "pragmatic", chain = 1),
      # binnned_data%>%mutate(model = "pragmatic", chain = 2),
      # binnned_data%>%mutate(model = "pragmatic", chain = 3),
      # binnned_data%>%mutate(model = "pragmatic", chain = 4),
      # binnned_data%>%mutate(model = "pragmatic", chain = 5),
      # binnned_data%>%mutate(model = "pragmatic", chain = 6)
      binnned_data%>%mutate(model = "pragmatic"),
      binnned_data%>%mutate(model = "global"),
      binnned_data%>%mutate(model = "flat"),
      binnned_data%>%mutate(model = "prior")
      )
  )

# saveRDS(plot_cor_model_pred, "../saves/model_cor.rds")
# plot_cor_model_pred <- readRDS( "../saves/model_cor.rds")

@@

plot_model_pred_flat <- model_pred_flat%>%
  group_by(alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

log_like_prag <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month)%>%
  left_join(plot_model_pred_prag)%>%
  mutate(like = ifelse(correct == 1, mean, 1 - mean),
         log_like_prag = log(like))%>%
  select(age, alignment,item,log_like_prag)

log_like_global <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month)%>%
  left_join(plot_model_pred_global)%>%
  mutate(like = ifelse(correct == 1, mean, 1 - mean),
         log_like_global = log(like))%>%
  select(age, alignment,item,log_like_global)

log_like_flat <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month)%>%
  left_join(plot_model_pred_flat)%>%
  mutate(like = ifelse(correct == 1, mean, 1 - mean),
         log_like_flat = log(like))%>%
  select(age, alignment,item,log_like_flat)

model_comp <- log_like_prag%>%
  left_join(log_like_global)%>%
  left_join(log_like_flat)%>%
  mutate(prag_vs_global = log_like_prag - log_like_global,
         prag_vs_flat = log_like_prag - log_like_flat)%>%
  na.omit(prag_vs_global,prag_vs_flat)%>%
  summarize(prag_vs_global = logSumExp(prag_vs_global),
            prag_vs_flat = logSumExp(prag_vs_flat))

log_like <- bind_rows(
  readRDS("../saves/log_like_chain1.rds")%>%mutate(chain = 1),
  readRDS("../saves/log_like_chain2.rds")%>%mutate(chain = 2),
  readRDS("../saves/log_like_chain3.rds")%>%mutate(chain = 3),
  readRDS("../saves/log_like_chain4.rds")%>%mutate(chain = 4),
  readRDS("../saves/log_like_chain5.rds")%>%mutate(chain = 5)
)

log_like_model<- log_like %>%
  group_by(model,parameter)%>%
  summarize(logP = logSumExp(log_like))%>%
  spread(parameter, logP)

log_like_chain<- log_like %>%
  group_by(chain, model,parameter)%>%
  summarize(logP = logSumExp(log_like))%>%
  spread(parameter, logP)

log_like_chain %>%
  group_by(model)%>%
  mutate(noise = round(noise,2),
         parameter_free = round(parameter_free,2))%>%
  summarise(range_param_free = paste(range(parameter_free)[1],range(parameter_free)[2], sep = " / "),
            range_noise = paste(range(noise)[1],range(noise)[2], sep = " / "))

log_like_2 <-  readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")%>%
  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
  filter(parameter == "log_like")%>%
  separate(value, into = c("na", "log_like"),sep = ",")%>%
  select(-na, -alignment)%>%
  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))

log_like_model_2 <- log_like_2%>%
  group_by(model,noise)%>%
  summarize(logP = logSumExp(log_like))

model_comp <- log_like_2%>%
  spread(model,log_like)%>%
  mutate(prag_vs_prag_global = pragmatics - pragmatics_global,
         prag_vs_flat_prior = pragmatics - flat_prior,
         prag_vs_prior_only = pragmatics - prior_only)%>%
  group_by(noise)%>%
  summarize(prag_vs_prag_global = logSumExp(prag_vs_prag_global),
            prag_vs_flat_prior = logSumExp(prag_vs_flat_prior),
            prag_vs_prior_only = logSumExp(prag_vs_prior_only))%>%
  gather(model,logP,-noise)

log_like_model_2_free <- log_like_model_2%>%
  filter(noise == "parameter_free")

@@

novel_bm <- readRDS("../saves/novelty_model.rds")

>>>>

# Packages & data

```{r}
library(tidyverse)
library(rwebppl)
#library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(bigmemory)
#library(langcog)

@@

# Model parameters

@@

#### summaries
item_params_summary <- item_params %>%
  group_by(item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

global_params_summary <- global_params %>%
  group_by (parameter,type)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

@@

@@

```{r}
plot_sem_know <- item_params_summary%>%
  select(-uci,-lci)%>%
  spread(parameter, -item) %>%
  left_join(expand.grid(
      age = unique(me_model_data$age),
      item = unique(me_model_data$item)), .) %>%
  mutate(sem_know = plogis(intercept + slope * age)) %>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

@@

```{r}
model_pred_prag <- readRDS("../saves/model_pred_prag.rds")

@@

x <- sample(1:length(unique(model_pred_prag$iteration)), 200)

plot_model_prag_line <- model_pred_prag%>%
  filter(iteration %in% x)%>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(data = plot_model_prag_line, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_colour_ptol(name = NULL)

@@

```{r}
ggsave("../graphs/pred_model_data.pdf", width = 10, height = 3, scale = 1)
```

@@

```{r}
# binnned_data <- data_comb%>%
#   group_by(subage, alignment, item)%>%
#   summarize(k = sum(correct), n = n())%>%
#   ungroup() %>%
#   mutate(a = 1 + k,
#          b = 1 + n - k,
#          data_mean = (a-1)/(a+b-2),
#          data_ci_lower  = qbeta(.025, a, b),
#          data_ci_upper = qbeta(.975, a, b),
#          age = factor(subage))%>%
#   select(-a,-b,-n,-k)
# 
# 
# cor_prag <- readRDS("../saves/model_pred_prag.rds")%>%
#   mutate(age = as.numeric(age) + min(data_comb$age_num),
#          age = cut(age, 
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model,alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_global <- readRDS("../saves/model_pred_global.rds")%>%
#   mutate(age = as.numeric(age) + min(data_comb$age_num),
#          age = cut(age, 
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_flat <- readRDS("../saves/model_pred_flat.rds")%>%
#   mutate(age = as.numeric(age) + min(data_comb$age_num),
#          age = cut(age, 
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_prior <- readRDS("../saves/model_pred_prior.rds")%>%
#   mutate(age = as.numeric(age) + min(data_comb$age_num),
#          age = cut(age,
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_model_pred <- bind_rows(
#    cor_prag,
#    cor_global,
#    cor_flat,
#    cor_prior
# )
# 
# 
# plot_cor_model_pred <- cor_model_pred %>%
#   left_join(
#     bind_rows(
#        binnned_data%>%mutate(model = "pragmatic"),
#        binnned_data%>%mutate(model = "global"),
#        binnned_data%>%mutate(model = "flat"),
#        binnned_data%>%mutate(model = "prior")
#       )
#   )

# saveRDS(plot_cor_model_pred, "../saves/corr_model_data.rds")

 plot_cor_model_pred <- readRDS( "../saves/model_cor.rds")

@@

```{r}
d_model_comp <- data_comb%>%
  select(-age)%>%
  mutate(age = round(age_month,2),
         item = as.character(item))%>%
  select(alignment, item, age, correct)

test_prag <- readRDS("../saves/model_pred_prag.rds")%>%
  filter(iteration == 1286 | iteration == 7185)%>%
  mutate(age = round(age,2))

saveRDS(test_prag,"../saves/test_prag.rds")

test_global <- readRDS("../saves/model_pred_global.rds")%>%
  filter(iteration == 1286 | iteration == 7185)%>%
  mutate(age = round(age,2))

saveRDS(test_global,"../saves/test_global.rds")

test_flat <- readRDS("../saves/model_pred_flat.rds")%>%
  filter(iteration == 1286 | iteration == 7185)%>%
  mutate(age = round(age,2))

saveRDS(test_flat,"../saves/test_flat.rds")

d_model_comp <- data_comb%>%
  select(-age)%>%
  mutate(age = round(age_month,2),
         item = as.character(item))%>%
  select(alignment, item, age, correct)

xxg <- xxg %>%
  mutate(age = round(age,2))

sort(unique(d_model_comp$age))

sort(unique(xx$age))

y <- xx %>%
  right_join(d_model_comp)

tail(y)

bind_rows(

  xx %>%
    right_join(d_model_comp)%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "prag",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

xxf %>%
    right_join(d_model_comp)%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "global",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like)

)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_global = prag - global) %>%
  summarise(prag_vs_global = sum(prag_vs_global))

@@

novel_bm <- readRDS("../saves_old/novelty_model.rds")
